### 2023-09-29 chapters/conclusion.tex
Updates to citation commands and footnotes

In the introductory \cref{chp:introduction} we laid out how, through human history, progress-driving technological development has always introduced new challenges and risks of error whether via misuse, misunderstanding or inherent limitations. We emphasized that machine learning comes with these same types of risk may in some cases may amplify their impacts and argued that uncertainty estimation is a key component in developing safe and reliable machine learning systems. We provided the motivational cases of recognition of stroke cases in emergency calls \cref{subsec:motivation-stroke-recognition} and automated medical coding \cref{subsec:motivation-medical-coding} and gave examples of potential sources of uncertainty and of how correctly quantifying uncertainty can improve the usefulness of such tools in practice. Finally, we ended the introduction by connecting machine learning reliability \cref{sec:machine-learning-reliability} and model calibration \cref{subsec:model-calibration} and defining different types of uncertainty \cref{subsec:types-of-uncertainty}.

\Cref{chp:technical-background} provided technical background only covered briefly by the individual studies. We first introduced uncertainty as a concept in the context of information and probability theory \cref{sec:information-theory}. Then, we defined the task of out-of-distribution detection and reviewed existing work on the problem \cref{\cref{sec:out-of-distribution-detection}}. Finally, we provided technical background for variational autoencoders \cref{sec:variational-autoencoders}.

>>>>

In the introductory \cref{chp:introduction} we laid out how, through human history, progress-driving technological development has always introduced new challenges and risks of error whether via misuse, misunderstanding or inherent limitations. We emphasized that machine learning comes with these same types of risk may in some cases may amplify their impacts and argued that uncertainty estimation is a key component in developing safe and reliable machine learning systems. We provided the motivational cases of recognition of stroke cases in emergency calls \cref{subsec:motivation-stroke-recognition} and automated medical coding \cref{subsec:motivation-medical-coding} and gave examples of potential sources of uncertainty and of how correctly quantifying uncertainty can improve the usefulness of such tools in practice. Finally, we ended the introduction by connecting machine learning reliability \cref{sec:machine-learning-reliability} and model calibration \cref{subsec:model-calibration} and defining different types of uncertainty \cref{subsec:understanding-uncertainty}.

\Cref{chp:technical-background} provided technical background only covered briefly by the individual studies. We first introduced uncertainty as a concept in the context of information and probability theory \cref{sec:uncertainty-information-theory}. Then, we defined the task of out-of-distribution detection and reviewed existing work on the problem \cref{sec:out-of-distribution-detection}. Finally, we provided technical background for variational autoencoders \cref{sec:variational-autoencoders}.

### 2023-09-29 chapters/discussion.tex
Updates to citation commands and footnotes

\lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \cite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}
\lesstodo[inline]{Discuss whether VAEs are even suitable for representation learning due to them minimizing a mutual information term in the ELBO (derive this form).}
\lesstodo[inline]{Discuss some recent work e.g. \cref{morningstar_density_2021}}

@@

\lesstodo[inline]{Are self-supervised speech representations useful for unsupervised uncertainty estimation? \cite{nava_stateconsistency_2021, nava_uncertaintyaware_2021} Within robotics but not really related.}
\lesstodo[inline]{Are self-supervised speech representations useful for unsupervised uncertainty estimation?}
% Since the main focus within self-supervised learning has been on improving downstream task performance, very limited work, if any, has investigated self-supervised representations in terms of uncertainty estimation. 
% However, in the context of medical applications where data can be abundant but labels are sparse, unsupervised uncertainty estimation is a very interesting direction for future work.
\lesstodo[inline]{OOD data: Generalization or detection (https://arxiv.org/pdf/2110.11334.pdf)?}

@@

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/calibration_curve_ensemble_and_all_models_uncalibrated.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/histogram_ensemble_and_single_model.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}
    \caption[Calibration curve for the uncalibrated stroke recognition model and empirical distribution of predicted probabilities.]{\subref{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated} \Cref{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated} shows the calibration curve for the uncalibrated ensemble model with median F1-score also reported in \cref{tab_retrospective:table3-occlusion-analysis} and \cref{fig_retrospective:figure1-roc-curve}. \subref{fig_discussion:histogram_ensemble_and_single_model} Histogram of predicted probabilities.}
\end{figure}

@@

\lesstodo[inline]{Discuss the calibration of the stroke model and report calibration curve.}
\lesstodo[inline]{Report the results of calibrating the stroke model using e.g. Platt scaling or Isotonic scaling.} % https://scikit-learn.org/stable/modules/calibration.html
\lesstodo[inline]{Maybe mention MultiQT paper \cite{havtorn_multiqt_2020}.}

>>>>

\lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \parencite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}
\lesstodo[inline]{Discuss whether VAEs are even suitable for representation learning due to them minimizing a mutual information term in the ELBO (derive this form).}
\lesstodo[inline]{Discuss some recent work e.g. \cref{morningstar_density_2021}}

@@

\lesstodo[inline]{Are self-supervised speech representations useful for unsupervised uncertainty estimation? \parencite{nava_stateconsistency_2021, nava_uncertaintyaware_2021} Within robotics but not really related.}
\lesstodo[inline]{Are self-supervised speech representations useful for unsupervised uncertainty estimation?}
% Since the main focus within self-supervised learning has been on improving downstream task performance, very limited work, if any, has investigated self-supervised representations in terms of uncertainty estimation. 
% However, in the context of medical applications where data can be abundant but labels are sparse, unsupervised uncertainty estimation is a very interesting direction for future work.
\lesstodo[inline]{OOD data: Generalization or detection (https://arxiv.org/pdf/2110.11334.pdf)?}

@@

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/calibration_curve_ensemble_and_all_models_uncalibrated.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/histogram_ensemble_and_single_model.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}
    \caption[Calibration curve for the uncalibrated stroke recognition model and empirical distribution of predicted probabilities.]{Calibration curve for the uncalibrated ensemble model with median F1-score also reported in \cref{tab_retrospective:table3-occlusion-analysis, fig_retrospective:figure1-roc-curve} (left) and the histogram of predicted probabilities (right).}
\end{figure}

@@

\lesstodo[inline]{Discuss the calibration of the stroke model and report calibration curve.}
\lesstodo[inline]{Report the results of calibrating the stroke model using e.g. Platt scaling or Isotonic scaling.} % https://scikit-learn.org/stable/modules/calibration.html
\lesstodo[inline]{Maybe mention MultiQT paper \parencite{havtorn_multiqt_2020}.}

### 2023-09-29 chapters/dummy_chapters/dummy_introduction.tex
Move table captions to top
Updates to citation commands and footnotes

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum \cite{adams1980hitchhiker}.

Mauris id quam non magna fermentum malesuada id mattis lorem. In a dapibus neque. Etiam lacus dui, malesuada ac eleifend imperdiet, imperdiet ut ipsum. Vestibulum id ultricies est. Phasellus augue mauris, semper a luctus vel, faucibus in risus. Fusce commodo augue quis elit sagittis non viverra turpis bibendum. Nunc placerat sem non sapien malesuada malesuada ullamcorper orci luctus \cite{adams1980hitchhiker}. Morbi pharetra ligula integer mollis mi nec neque ultrices vitae volutpat leo ullamcorper. In at tellus magna. Curabitur quis posuere purus. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Suspendisse tristique placerat feugiat. Aliquam vitae est at enim auctor ultrices eleifend a urna. Donec non tincidunt felis. Maecenas at suscipit orci. See \cref{myFigure}.
\begin{figure}
    \centering
        \missingfigure[figwidth=6cm]{}
    \caption[Short caption to special figure]{This is my special figure. Aliquam ultricies, arcu quis tempor rhoncus, tellus nisl tempus justo, condimentum tempor erat odio ac purus. Integer quis ipsum felis. Aliquam volutpat, leo ac consequat egestas, lectus lacus adipiscing quam, id iaculis dolor quam in erat. Phasellus tempor interdum arcu quis vestibulum}
    \label{myFigure}
\end{figure}

@@

\begin{table}
    \centering
        \begin{tabular}{c | r l}
            h & h & h \\
            e & e & e \\
        \end{tabular}
    \caption{This is a caption to the table}
    \label{myTable}
\end{table}

>>>>

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum \parencite{adams1980hitchhiker}.

Mauris id quam non magna fermentum malesuada id mattis lorem. In a dapibus neque. Etiam lacus dui, malesuada ac eleifend imperdiet, imperdiet ut ipsum. Vestibulum id ultricies est. Phasellus augue mauris, semper a luctus vel, faucibus in risus. Fusce commodo augue quis elit sagittis non viverra turpis bibendum. Nunc placerat sem non sapien malesuada malesuada ullamcorper orci luctus \parencite{adams1980hitchhiker}. Morbi pharetra ligula integer mollis mi nec neque ultrices vitae volutpat leo ullamcorper. In at tellus magna. Curabitur quis posuere purus. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Suspendisse tristique placerat feugiat. Aliquam vitae est at enim auctor ultrices eleifend a urna. Donec non tincidunt felis. Maecenas at suscipit orci. See \cref{myFigure}.
\begin{figure}
    \centering
        \missingfigure[figwidth=6cm]{}
    \caption[Short caption to special figure]{This is my special figure. Aliquam ultricies, arcu quis tempor rhoncus, tellus nisl tempus justo, condimentum tempor erat odio ac purus. Integer quis ipsum felis. Aliquam volutpat, leo ac consequat egestas, lectus lacus adipiscing quam, id iaculis dolor quam in erat. Phasellus tempor interdum arcu quis vestibulum}
    \label{myFigure}
\end{figure}

@@

\begin{table}
    \caption{This is a caption to the table}
    \centering
        \begin{tabular}{c | r l}
            h & h & h \\
            e & e & e \\
        \end{tabular}
    \label{myTable}
\end{table}
